|

### 2020-06-14 appendix/appendix_final.Rmd
commit review mig 1

@@

@@

```{r, echo=FALSE, include=FALSE}
load('../dataset/dataCoefs.RData')
```

@@

export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2, 
                        show.p.overall = F, show.all = T),
          caption = "Descriptive Statistics of Moderators")
```

@@

## Per Capita Expenditure x N

@@

## Per Capita Expenditure x Log of Lower House Size

@@

## Per Capita Expenditure x Size of the Upper House

@@

## Log of Expenditure Per Capita x Size of the Lower House

@@

## Log of Expenditure Per Capita x Log of Lower House Size

@@

## Log of Expenditure Per Capita x Size of Upper House

@@

## Expenditure as a Percentage of the GDP x Lower House Size

@@

\newpage
## Expenditure as a Percentage of the GDP x Log of Lower House Size

@@

\newpage
## Expenditure as a Percentage of the GDP x Upper House Size

@@

## ExpPC x N

@@

\newpage
## ExpPC x logN

@@

## ExpPC x K

@@

\newpage
## logExpPC x N

@@

\newpage
## logExpPC x logN

@@

## logExpPC x K

@@

## PCTGDP x N

@@

## PCTGDP x logN

@@

## PCTGDP x K

@@

```{r, echo=F, warning=F, error=F, message=F}
coefs <- tibble(
  ` ` = c("Intercept", "Indepvar: N","Indepvar: logN", "Year", "Published: No", "Elecsys: Non-Majoritarian",
    "Method: Panel", "Method: IV", "Method: RDD", "AggLevel: States", "Location: World"))

@@

```{r, echo=F, warning=F,error=F,message=F}
coefs <- tibble(
  ` ` = c("Intercept", "Indepvar: N","Indepvar: logN", "Year", "Published: No", "Elecsys: Non-Majoritarian",
    "Method: Panel", "Method: IV", "Method: RDD", "AggLevel: States", "Location: World")
)

@@

# The theory behind the Meta Analysis

@@

## Graph functions code

>>>>

# Load datasets
load('../dataset/dataCoefs.RData')

@@

  # Build plot
  p <- mod2 %>%
    ggplot(aes(y = reorder(studlab2,TE), 
               x = TE, xmin = lower, xmax = upper)) +
    geom_point(aes(color = group)) +
    geom_errorbarh(aes(color = group), 
                   height = 0.1) +
    scale_color_manual(values = c("#000000", "#8b0000")) +
    scale_x_continuous(limits = c(-1.1*limg, 1.1*limg)) +
    scale_y_discrete(
      labels = function(x) 
        str_replace(x, "_[0-9]*$", "")) + 
    geom_vline(xintercept=0, 
               color="#000000", linetype="dashed") +
    labs(x = "",
         y = "") + 
    facet_grid(group~., scales = "free", space = "free") + 
    labs(caption = capt,
         title = ttl) +
    theme_minimal() %+replace%
    theme(strip.text.y = element_blank(),
          legend.position = "none",
          axis.text.y = element_text(size = .8*lsize, 
                                     hjust = 1),
          axis.text.x = element_text(size = .6*lsize, 
                                     hjust = 1.1),
          plot.caption = element_text(size=lsize),
          plot.title.position = 'plot', 
          plot.title = element_text(hjust = 0.5, 
                                    face = 'bold',
                                    margin=margin(0,0,10,0)),
          panel.grid.major = element_blank())
  return(p)
}
```

@@

@@

#export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2,
#                     show.p.overall = F, show.all = T),
#          caption = "Descriptive Statistics of Moderators")

descrTable(~.-usemeta2, aux, y = aux$usemeta2,
           show.p.overall = F, show.all = T)
```

@@

## Lower House Size and Expenditure per Capita

@@

## Log Lower House Size and Expenditure per Capita

@@

## Upper House Size and Expenditure per Capita

@@

## Lower House Size and Log Expenditure Per Capita

@@

## Log of Lower House Size and Log of Expenditure Per Capita

@@

## Log of Upper House Size and Log of Expenditure Per Capita

@@

## Lower House Size and Expenditure as Percentage of GDP

@@

## Log Lower House Size and Expenditure as Percentage of GDP

@@

## Upper House Size and Expenditure as Percentage of GDP

@@

## Lower House Size and Expenditure Per Capita

@@

\newpage
## Log of Lower House Size and Expenditure Per Capita

@@

## Upper House Size and Expenditure Per Capita

@@

\newpage
## Lower House Size and Log of Expenditure Per Capita

@@

\newpage
## Log of Lower House Size and Log of Expenditure Per Capita

@@

## Upper House Size and Log of Expenditure Per Capita

@@

## Lower House Size and Expenditure as Percentage of GDP

@@

## Log of Lower House Size and Expenditure as Percentage of GDP

@@

## Upper House Size and Expenditure as Percentage of GDP

@@

```{r, echo=F, warning=F, error=F, message=F}
coefs <- tibble(
  ` ` = c("Intercept", 
          "Indepvar: N",
          "Indepvar: logN", 
          "Year", 
          "Published: No", 
          "Elecsys: Non-Majoritarian",
          "Method: Panel", 
          "Method: IV", 
          "Method: RDD", 
          "AggLevel: States", 
          "Location: World"))

@@

```{r, echo=F, warning=F,error=F,message=F}
coefs <- tibble(
  ` ` = c("Intercept", 
          "Indepvar: N",
          "Indepvar: logN", 
          "Year", 
          "Published: No", 
          "Elecsys: Non-Majoritarian",
          "Method: Panel", 
          "Method: IV", 
          "Method: RDD", 
          "AggLevel: States", 
          "Location: World")
)

@@

# The Theory behind the Meta Analysis

@@

## Function for generate the Meta-Analytic Figures
